### 2017-05-16 README.Rmd
cite nesRdata, point to raw csv

This respository contains a digitally transcribed copy ([nes_data.csv](https://github.com/ReproducibleQM/NES/blob/master/nes_data.csv)) of the National Eutrophication Survey (NES) dataset. The original data can be found in the `archival_pdfs` folder or by searching: https://www.epa.gov/nscep

@@

>>>>

This respository contains a digitally transcribed copy ([nes_data.csv](https://github.com/ReproducibleQM/NES/raw/master/nes_data.csv)) of the National Eutrophication Survey (NES) dataset. The original data can be found in the `archival_pdfs` folder or by searching: https://www.epa.gov/nscep

@@

Stachelek, J. (2017). nesRdata: National Eutrophication Survey Data Package. R package version 0.1. https://github.com/jsta/nesRdata
